---
title: "Rpack - Project Presentation"
author: "David Nathan Ohayon"
date: "2023-05-22"
output: 
  ioslides_presentation:
    #incremental: true
    widescreen: true
    fullscreen: true
    smaller: true
    logo: ../data/UNIGE.png
    css: styles.css
    revealjs::revealjs_presentation:
      theme: night
      center: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, echo = FALSE}
library(ProteomicsTools)
```


## Context of the package {.flexbox .vcenter}

- Question:
  - Is there a bias between one given method and one given protein ?
- 5 methods of proteomic extraction in order to compare those methods:
  - RIPA
  - NucleoSpin
  - Tris.HCl
  - Triton.X100
  - Urea
- The same cell has been lysed with those methods (a human melanoma cell line [G-361])
- Protein abundance have been estimated using MS technology
  - Goals of the package:
    - Analyze proteomic data
    - Compare methods of extraction
    - Visualization tools
 

--- 

### Input Table (log2 protein abundances)

```{r}
library(DT)
rownames(log2) <- log2[,1]
datatable(log2[,-1], options = list(scrollX = TRUE, scrollY = "350px"))
```
  
---

### Mined Data from NeXtProt

```{r}
library(DT)
rownames(big) <- big[,1]
datatable(big[,-1], options = list(scrollX = TRUE, scrollY = "350px"))
```

---

### MultiDimensional Scaling Plot (visualization tool)

```{r, echo = TRUE, highlight=FALSE, warning=FALSE, message=FALSE, fig.width=12, fig.height=5, dpi=72}
myMDSplot(log2)
```


---

### Heatmap of the log2 data
<div style="height: 470px; overflow: scroll;">
```{r, echo = TRUE, highlight=FALSE, warning=FALSE, message=FALSE, fig.width=13, fig.height=200, dpi=72}
library(ProteomicsTools)
heatmap_maker(log2[,-1])
```
</div>

---

### Internal Function to create the replicate variable

```{r, echo=FALSE, warning=FALSE, message=FALSE}
datatable(replicates_factor(log2), options = list(scrollX = TRUE, scrollY = "350px"))
```

---

### Pairwise t-test for each pair of method

```{r}
datatable(ttest, options = list(scrollX = TRUE, scrollY = "350px"))
```

---

### Internal Function: change numeric p-value into logical 

```{r}
datatable(reformat_table(ttest), options = list(scrollX = TRUE, scrollY = "350px"))
```

---

### Internal Function to correct my pairs of methods

```{r, echo=FALSE, warning=FALSE, message=FALSE}
datatable(col_sorted(ttest), options = list(scrollX = TRUE, scrollY = "350px"))
```

---

### Enrichment analysis of my pairwise t-tests 

```{r}
datatable(ftest, options = list(scrollX = TRUE, scrollY = "350px"))
```

---

### Internal Function: Computes mean of the replicates 

```{r, echo=FALSE, warning=FALSE, message=FALSE}
datatable(mean_function(replicates_factor(log2)), options = list(scrollX = TRUE, scrollY = "350px"))
```

---

### Pairwise foldchange for each pair of method

```{r}
datatable(foldc, options = list(scrollX = TRUE, scrollY = "350px"))
```

---

### VolcanoPlots for each method, with extra highlight 
<div style="height: 470px; overflow: scroll;">
```{r, echo = TRUE, highlight=FALSE, warning=FALSE, message=FALSE, fig.width=40, fig.height=5, dpi=72}
volcano_all(ttest, foldc, big, "TMregions", path = "../examples/")

```
</div>

---

### Isolate volcano plot

```{r, echo = TRUE, highlight=FALSE, warning=FALSE, message=FALSE, fig.height=4}
volcano_maker(ttest, foldc, big, "TMregions", path = "../examples/")
```

---

### Venn Diagram for each method

```{r, echo = TRUE, highlight=FALSE, warning=FALSE, message=FALSE, fig.width=13.5, fig.height=5.5, dpi=72}
myvenndiagram(ttest, path = "../examples/")
```

---

### DotPlot to visualize enrichment analysis

```{r, echo = TRUE, highlight=FALSE, fig.width=10, fig.height=5.2}
fisher_dotplot(ftest, path = "../examples/")
```


## Quick conclusion

This package has turned out really helpful to:

- Understand and advance my studies
- Give me new ideas about my project 

Around R:

- Has shown me new possibilities of R
- Learnt new programmatic approaches (apply, melting table...)
- Can surely optimize my functions

